---
title: "Storyboard example"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---


```{r setup, include= FALSE}
library(sp)
library(sf)
library(geojsonio)
library(leaflet)
library(leaflet.extras)
library(RColorBrewer)
library(readxl)
library(dplyr)
library(mapview)
library(hablar)
library(tidyr)
library(htmlwidgets)
library(tidyverse)

############ PREPARE RAW DATA AND BOUNDARY FILE
#####
LUI_main<- read_excel("Data/Cluster analysis v1.8 JH for WPIE.xlsx", sheet = 1)
LUI_sub<- read_excel("Data/Cluster analysis v1.8 JH for WPIE.xlsx", sheet = 2)

# Clean up 
LUI_main<-LUI_main[-1,-1]
LUI_sub<- LUI_sub[c(-1,-575:-579),-1]  

# Match by PC code
combi <- merge(LUI_sub,LUI_main,by = "PC code", all.y = T)
combi <- combi[,-9]

#remame cols so it's easier for later
colnames(combi) <- c("pcon19cd", "pcon19nm", "Spending power", "Dependency", "Crime", "Deprivation", "Health", "Blight", "Levelling-Up index")

# JSON MAP - https://geoportal.statistics.gov.uk/datasets/westminster-parliamentary-constituencies-december-2019-boundaries-uk-buc
# Import json
pc2019 <- geojson_sf("https://opendata.arcgis.com/datasets/4c191bee309d4b2d8b2c5b94d2512af9_0.geojson")


# set colour pallette
pallette <- c("#660a0b", "#8d443a","#b0776e", "#d1aba5", "#efe2e0")


#####
# MAP 1 - overall LU indicator
#####
map1<- combi[,c(1,2,9)]

#merge with master 
pc_data1 <- merge(pc2019,map1, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data1$ntile <- ntile(pc_data1$`Levelling-Up index`, 5)  

#relabel quintile
# change values to categories
pc_data1$ntile[pc_data1$ntile == 1] <- "1 (lowest rank)"
pc_data1$ntile[pc_data1$ntile == 2] <- "2"
pc_data1$ntile[pc_data1$ntile == 3] <- "3"
pc_data1$ntile[pc_data1$ntile == 4] <- "4"
pc_data1$ntile[pc_data1$ntile== 5] <- "5 (highest rank)"

factpal <- colorFactor(pallette, domain = pc_data1$ntile) 

#Label
labels1 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data1$pcon19nm.x, round(pc_data1$`Levelling-Up index`,0)) %>% lapply(htmltools::HTML)

######
# MAP 2 - spending power
######

#select for map 2
map2<- combi[,c(1,2,3)]

#merge with master 
pc_data2 <- merge(pc2019,map2, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data2$ntile <- ntile(pc_data2$`Spending power`, 5)  

#relabel quintile
# change values to categories
pc_data2$ntile[pc_data2$ntile == 1] <- "1 (lowest rank)"
pc_data2$ntile[pc_data2$ntile == 2] <- "2"
pc_data2$ntile[pc_data2$ntile == 3] <- "3"
pc_data2$ntile[pc_data2$ntile == 4] <- "4"
pc_data2$ntile[pc_data2$ntile== 5] <- "5 (highest rank)"

factpal2 <- colorFactor(pallette, domain = pc_data2$ntile) #"Set3 is a colorbrewer preset https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html

#this makes the hover over popup label
labels2 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data2$pcon19nm.x, round(pc_data2$`Spending power`,0)) %>% lapply(htmltools::HTML)


#####
# MAP 3 - dependency
#####

#select for map 3 
map3<- combi[,c(1,2,4)]

#merge with master 
pc_data3 <- merge(pc2019,map3, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data3$ntile <- ntile(pc_data3$Dependency, 5)  

# change values to categories
pc_data3$ntile[pc_data3$ntile == 1] <- "1 (lowest rank)"
pc_data3$ntile[pc_data3$ntile == 2] <- "2"
pc_data3$ntile[pc_data3$ntile == 3] <- "3"
pc_data3$ntile[pc_data3$ntile == 4] <- "4"
pc_data3$ntile[pc_data3$ntile== 5] <- "5 (highest rank)"

factpal3 <- colorFactor(pallette, domain = pc_data3$ntile) #"Set3 is a colorbrewer preset https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html

#this makes the hover over popup label
#this makes the hover over popup label
labels3 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data3$pcon19nm.x, round(pc_data3$Dependency,0)) %>% lapply(htmltools::HTML)

#####
## MAP 4 - Crime
#####

#select for map 3 
map4<- combi[,c(1,2,5)]

#merge with master 
pc_data4 <- merge(pc2019,map4, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data4$ntile <- ntile(pc_data4$Crime, 5)  

# change values to categories
pc_data4$ntile[pc_data4$ntile == 1] <- "1 (lowest rank)"
pc_data4$ntile[pc_data4$ntile == 2] <- "2"
pc_data4$ntile[pc_data4$ntile == 3] <- "3"
pc_data4$ntile[pc_data4$ntile == 4] <- "4"
pc_data4$ntile[pc_data4$ntile== 5] <- "5 (highest rank)"

factpal4 <- colorFactor(pallette, domain = pc_data4$ntile) #"Set3 is a colorbrewer preset https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html

#this makes the hover over popup label
labels4 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data4$pcon19nm.x, round(pc_data4$Crime,0)) %>% lapply(htmltools::HTML)

#####
## MAP 5 - Deprivation
#####

#select for map 3 
map5<- combi[,c(1,2,6)]

#merge with master 
pc_data5 <- merge(pc2019,map5, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data5$ntile <- ntile(pc_data5$Deprivation, 5)  

# change values to categories
pc_data5$ntile[pc_data5$ntile == 1] <- "1 (lowest rank)"
pc_data5$ntile[pc_data5$ntile == 2] <- "2"
pc_data5$ntile[pc_data5$ntile == 3] <- "3"
pc_data5$ntile[pc_data5$ntile == 4] <- "4"
pc_data5$ntile[pc_data5$ntile== 5] <- "5 (highest rank)"

factpal5 <- colorFactor(pallette, domain = pc_data5$ntile) #"Set3 is a colorbrewer preset https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html

#labels
labels5 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data5$pcon19nm.x, round(pc_data5$Deprivation,0)) %>% lapply(htmltools::HTML)

##### 
## MAP 6 - Health
##### 
# Wales is missing

#select for map 6
map6<- combi[,c(1,2,7)]

#merge with master 
pc_data6 <- merge(pc2019,map6, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data6$ntile <- ntile(pc_data6$Health, 5)  

# change values to categories
pc_data6$ntile[pc_data6$ntile == 1] <- "1 (lowest rank)"
pc_data6$ntile[pc_data6$ntile == 2] <- "2"
pc_data6$ntile[pc_data6$ntile == 3] <- "3"
pc_data6$ntile[pc_data6$ntile == 4] <- "4"
pc_data6$ntile[pc_data6$ntile== 5] <- "5 (highest rank)"

factpal6 <- colorFactor(pallette, domain = pc_data6$ntile) #"Set3 is a colorbrewer preset https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html

#this makes the hover over popup label
labels6 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data6$pcon19nm.x, round(pc_data6$Health,0)) %>% lapply(htmltools::HTML)

#####
## MAP 7 - Blight
#####

#select for map 6
map7<- combi[,c(1,2,8)]

#merge with master 
pc_data7 <- merge(pc2019,map7, by.y= "pcon19cd", by.x="pcon19cd", all.x= T)

# a new column for ntile
pc_data7$ntile <- ntile(pc_data7$Blight, 5)  

# change values to categories
pc_data7$ntile[pc_data7$ntile == 1] <- "1 (lowest rank)"
pc_data7$ntile[pc_data7$ntile == 2] <- "2"
pc_data7$ntile[pc_data7$ntile == 3] <- "3"
pc_data7$ntile[pc_data7$ntile == 4] <- "4"
pc_data7$ntile[pc_data7$ntile== 5] <- "5 (highest rank)"

factpal7 <- colorFactor(pallette, domain = pc_data7$ntile) #"Set3 is a colorbrewer preset https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html

#this makes the hover over popup label
labels7 <- sprintf("<strong>%s</strong><br/>%s ranking<sup></sup>", pc_data7$pcon19nm.x, round(pc_data7$Blight,0)) %>% lapply(htmltools::HTML)

```


### The first map looks at the overall Levelling-Up Index. {data-commentary-width=400}


```{r}
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data1, stroke = T, color = ~factpal(pc_data1$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels1,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal, values = pc_data1$ntile, labels=pc_data1$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T) 
```

*** 
Some text about things.

    
### The second map looks at spending power. {data-commentary-width=400}

```{r}
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data2, stroke = T, color = ~factpal(pc_data2$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels2,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal2, values = pc_data2$ntile, labels=pc_data2$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T) 
```

*** 
Some more text about things.


### The third maps looks at dependency. {data-commentary-width=400}
 

```{r}
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data3, stroke = T, color = ~factpal(pc_data3$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels3,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal3, values = pc_data3$ntile, labels=pc_data1$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T)
 
```

*** 
Some more text about things.


### The fourth map looks at crime. {data-commentary-width=400}


```{r}
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data4, stroke = T, color = ~factpal(pc_data4$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels4,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal4, values = pc_data4$ntile, labels=4$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T) 


```

*** 
Some more text about things.

### The fifth map looks at deprivation. {data-commentary-width=400}

```{r}
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data5, stroke = T, color = ~factpal(pc_data5$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels5,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal5, values = pc_data5$ntile, labels=pc_data5$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T)
```

*** 
Some more text about things.


### The sixt maps looks at health. {data-commentary-width=400}


```{r}
library(leaflet)
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data6, stroke = T, color = ~factpal(pc_data6$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels6,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal6, values = pc_data6$ntile, labels=pc_data6$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T) 

```


*** 
Some more text about things.

### The seventh map looks at blight. {data-commentary-width=400}

```{r}
library(leaflet)
library(leaflet)
leaflet() %>% setView(-1.161877,52.350304, 6) %>% #setView gives centre coordinates and zoom level
  setMapWidgetStyle(list(background = "white")) %>%  addProviderTiles(providers$CartoDB.Positron, providerTileOptions(opacity = 1) ) %>% 
  
  addPolygons(data = pc_data7, stroke = T, color = ~factpal(pc_data7$ntile),opacity = 1, fillOpacity = 0.9, weight=1, label = labels7,  highlight= highlightOptions(color="white", weight=2, bringToFront= T))  %>% 
  
  addLegend(pal = factpal7, values = pc_data7$ntile, labels=pc_data7$ntile, opacity=1, position = "bottomright", title="Ranking quintiles") %>% 
  removeDrawToolbar(clearFeatures = T) 


```

*** 
Some more text about things.

